Motion Planning and Robust Decentralized Fault-Tolerant Tracking Control of Hybrid UAVs and Biped Robots Team System for Search and Rescue Usage

### 2022-12-14 paper/paper.tex
Revise paper

\begin{figure}[htbp]
\centering
\includegraphics[scale=.15]{fig/sys.png}\caption{The system architecture of agent in URTS. The 2 blocks on left hand side are used to convert the low-level sensor information into high-level information, such as map $\mathcal{C}$, current position $q_{start}$ and object information. The 5 blocks on right hand side are the flow of an agent performing a S\&R mission. From the top to the bottom, it is the decision of the task position, the planning of the path, the decision of the behavior, the planning of the local motion trajectory, and the low-level tracking control.}%
\label{fig:sys}
\end{figure}

\subsection{Task Allocation}
In the URTS, it can be expected that each agent $\alpha_{i,j}$ will be assigned to several specific tasks, such as searching a specific area, or delivering supplies to disaster area, etc. However, the number of agents and tasks is more than one, and each agent has different capabilities (e.g., moving speed or load capacity) and status (e.g., the relative distance between the agent itself and the target or the amount of supplies carried), and each task has different characteristics (e.g., urgency, position, amout of supplies needed). Therefore, the results of task allocation can be "good or bad", which leads us to finding the optimal allocation. This problem is referred to a task allocation problem or multi-robot task allocation problem. A problem formulation and a mathematical model of problem can be found in \cite{khamis2015multi}. Although many different formulations and models have been employed to solve the task allocation problem, the common goal is to find a set of agent-task pairs to achieve a specific cost function. In this paper, we assume that the tasks have been properly assigned so that every agent knows a goal $q_{goal}$ it needs to go at every moment.
% $(\mathcal{G})_n, n\in\mathbb{Z}\cap[1, N], N\in\mathbb{Z}^+$
\textit{
    \begin{remark}
        This block is like a commander since it is used to assign task for agents. Thus, if the real S\&R system has human experts as commanders, he can replace its job or make decisions together with it to maximize the rescue value.
    \end{remark}
}
\textit{
    \begin{remark}
        Although each agent has its own team, agents can also work across teams. For example, if the result given by the task allocation algorithm contains the agent-task pairs $(\alpha_{1,5},T_1)$ and $(\alpha_{2,2},T_1)$, then the agent $\alpha_{1,5}$ in team 1 and the agent $\alpha_{2,2}$ in team 2 will execute task $T_1$ together. 
    \end{remark}
}

@@

\subsection{Behavior Layer}
% Since UAVs and robots are real physical systems, they must interact with the environment through a behavior so that they can move and act in the physical world.
Path planning tells agents where to go but not how since we regard the agent as a point. Taking robot as an example, it may walk, run, climb, or jump to follow the path $(\sigma_n)$ according to real scenario. These behaviors with changing position are classified as "moving" behavior in this paper. Besides, the agents in the hybrid URTS do not always moving. Somtimes they have to suspend to take an action (e.g., getting and putting supplies, rotating in place to collect more environment information) or deal with some unexpected situations (e.g., no path found, the robot falls). These behaviors without changing position are classified as "action" behavior in this paper. More behaviors can be added so that the agent can have more ways to act with environment but there must have a corresponding behavior every moment otherwise the agent will lose control. The sequence of these behaviors can be expressed as:
\begin{equation}
    (\beta_n), n\in\mathbb{Z}\cap[1,k_f], \beta_n\in\mathcal{B}
\end{equation}
where $\mathcal{B}$ is the set of behaviors. It means that the path $(\sigma_n)$ is divided into many segments and each segment corresponds to a specific behavior. By the object information in Fig. \ref{fig:sys}, an appropriate behavior can be judged. However, it will be a rather complicated project, so this article only gives the structure of the behavior set. The behavior set $\mathcal{B}$ of agent in URTS can be roughly discribed in Fig. \ref{fig:behavior}.

\begin{figure*}[htbp]
    \centering
    \includegraphics[scale=.12]{fig/behavior.png}\caption{The structure of behavior layer. (a) The behavior set of each agent in URTS. The leaves of the tree structure are the possible behaviors an agent can take. The behavior to be took at every moment by each agent will be decided in this block. For UAVs, the moving behavior set is predefined in (b). For robots, the moving behavior set is predefined in (c). (b) The moving behavior set of each UAV. (c) The moving behavior set of each robot.}%
    \label{fig:behavior}
\end{figure*}

\subsection{Local Motion Planning}
After a specific behavior is determined, the next step is to design a motion to achieve the specific behavior. Local motion planning block is like path planning block but with smaller scale and higher resolution and precision. Collision checking is needed since we consider agent as a point in path planning block but it is a real mechanical body here. Furthermore, the kinodynamic constraint is handled in this block. Although motion planning and path planning are separated into two blocks, the technologies involved are similar and often with the same notion in other literature. Therefore, the output of this block is also a path $r[k]$ (It is also a sequence but this article uses the notation of discrete signal $r[k]$ to represent it). The flowchart of local motion planning block is shown in Fig. \ref{fig:LMP}.
\begin{figure*}[htbp]
    \centering
    \includegraphics[scale=.12]{fig/LMP.png}\caption{The flowchart of local motion planning. (a) The local motion planning of each agent in URTS . The corresponding motion planning of an agent will be executed according to the behavior determined by the behavior layer. The exception terminator in figure represents an exceptional condition that performs unconsidered behaviors. The reference path $r[k]$ is a sequence (or discrete signal) designed by a specific behavior block. For UAVs, the moving block is predefined in (b). For robots, the moving block is predefined in (c). (b) The moving block of each UAV where the flying block is predefined in Fig. \ref{fig:FandW} (c) The moving block of each robot where the walking block is predefined in Fig. \ref{fig:FandW}}
    \label{fig:LMP}
\end{figure*}

@@

\section{system description of UAVs and biped robots in URTS}
In order to design a reference trajectory $r(t)$ for the motion of UAV and robot in URTS, their dynamic models must be given first. After the system description of UAV and robot in URTS, the motion planning of flying and walking as shown in Fig. \ref{fig:FandW} will be discussed subsequently and separately in the next two subsections.
\begin{figure*}[htbp]
    \centering
    \includegraphics[scale=.12]{fig/FandW.png}\caption{The flowchart of flying block and walking block in \ref{fig:LMP}. In both blocks, a smoothed path is obtained by post-processing first. Then the respective motion of behavior is designed.
    %The final outputs of flying block and walking block are all desired reference path $r[k]$, but its value and dimension will vary according to the dimension of the system model.
    (a) The flying block of each UAV. By combining the position path $(\sigma'_n)$ and setting $\phi_d=0$ (let UAV fly without spinning), we have the reference path $r[k]$.
    (b) The walking block of each robot. Follow the process in Section IV-B, we have the reference path $r[k]$.}
    \label{fig:FandW}
\end{figure*}
Before the discussion of the motion planning of these two behaviors, the following assumption is maded.
\textit{
    \begin{assumption} \label{asm:cc again}
        The space between obstacles is large enough to eliminate the need for collision checking again, and the average speed of agents is slow enough to ignore the nonholonomic constraints (the velocity and acceleration constraints).
    \end{assumption}
}
However, for these two behaviors, there exists an inevitable holonomic constraint on the curvature of local motion. Although an accurate reference trajectory without breaking the curvature constraint can be designed, it is not easy to solve this problem. Additionally, it is not nessasry for these two behaviors in URTS since they are uesd to move from one location to another while the effect of error during moving caused by breaking the curvature constraint is relatively insignificant. At the same time, the \textit{Assumption \ref{asm:cc again}} makes sure this error will not cause collision. As an alternative, this problem can be handled by curve fitting which can be regarded as a post-process of the path $(\sigma_n)$. The post-process will appear in the begining of motion planning process of these two behaviors as shown in Fig. \ref{fig:FandW}.

@@

Now, suppose the UAV flying behavior occurs between time step $k_1$ and $k_2$, that is, $\beta_n=\mathit{flying}, n\in\mathbb{Z}\cap[k_1,k_2]$. The corresponding path $(\sigma_n), n\in\mathbb{Z}\cap[k_1,k_2]$ will be smoothed first by linear interpolation and then by cubic spline interpolation, which gives the smoothed path $(\sigma_n'), n\in\mathbb{Z}\cap[k_1,k_2+D(k_2-k_1)], \sigma_n'\in\mathbb{R}^3$, where $D\in\mathbb{Z}$ is the interpolation density. Then, $(\sigma_n')$ will be the position reference path $[
    x_r[k], y_r[k], z_r[k]
]^T$. Subsequently, we consider the orientation reference path, row angle $\phi_r[k]$, pitch angle $\theta_r[k]$ and yaw angle $\psi_r[k]$. $\phi_r[k]$ is set to zero since no need for spinning when flying. $\theta_r[k]$ and $\psi_r[k]$ cannot be set beforehand since UAV is an underactuated system, which will be discussed in the next section. Finally, the reference path $r[k]$ of UAV can be obtained by combining them together, i.e., $r[k] = [
    x_r[k], y_r[k], z_r[k], \psi_r[k]
]^T\in\mathbb{R}^{4}$. The flowchart is shown in Fig. \ref{fig:FandW}.

@@

With 3D-LIPM, we can significantly reduce the amount of computation. Let us define the body frame of biped robot as $\{ \widehat{X_b}, \widehat{Y_b}, \widehat{Z_b} \}$ as in \cite{ourrobot}. Taking the forward direction of biped robot as $\widehat{X_b}$ direction, the left direction as $\widehat{Y_b}$ direction, and the torso direction as $\widehat{Z_b}$ direction in body frame, "Falling" means the moments on the robot in $\widehat{X_b}$ and $\widehat{Y_b}$ direction are not zero. More accuately, the biped robot will not fall if the zero moment point (ZMP) lies in the support polygon, i.e., the convex hull of face of supported foots. The ZMP in $\widehat{X_b}$ direction can be discribed as \cite{huang2001planning} (The ZMP in the $\widehat{Y_b}$ direction is the same form):
\begin{equation} \label{eq:x_zmp}
    x_{zmp} = \frac{\sum_{i=1}^{12} (m_i(\ddot{z}_i+g)x_i - m_i\ddot{x}_iz_i - I_{iy}\ddot{\Omega}_{iy})}
                   {\sum_{i=1}^{12} m_i(\ddot{z}_i+g)}
\end{equation}
where $m_i$ is the CoM, $x_i, z_i$ are the linear position components, $I_{iy}$ is the inertial component, and $\ddot{\Omega}_{iy}$ is the angular acceleration component of link $i$. However, it is difficult to directly calculate the analytical solution of $q_r(t)$ through (\ref{eq:x_zmp}). Since there exists a complex coordinate transformation between $q_r(t)$ and $x_i, z_i, \ddot{\Omega}_{iy}$. At the same time, it is necessary to ensure that $x_{zmp}$ falls in the support polygon which also has a relationship with $q_r(t)$. To simplify this complex problem, an approximate solution can be derived through 3D-LIPM. We find CoM reference first and then obtain $q_r(t)$ by using inverse kinematic (IK) with given step size, step height, step period and CoM height. Many researchers have used this method to avoid complex calculations for ZMP of the actual robot dynamic model. Although there exists a model error between the actual dynamic model and 3D-LIPM, the design process will be more simple. The overall process is shown in Fig. \ref{fig:FandW}.
% \begin{figure}[htbp]
%     \centering
%     \includegraphics[scale=.3]{fig/walking.pdf}\caption{flowchart of biped robot walking}%
%     \label{fig:walking}
% \end{figure}

@@

To complete the design of reference trajectory $r(t)$ of each agent, a D/A converter is used to transform the reference path $r[k]$ (output of local motion planning) into a continuous signal $r'(t)$ as shown in Fig. \ref{fig:tracking}. For UAV, we get $r'(t) = [x_r, y_r, z_r, \psi_r]^T\in\mathbb{R}^{4}$. Besides, for an UAV in hybrid URTS, it can be seen that the control input $u(t)=[f_u^T, \tau_u^T]^T = [f_x, f_y, f_z, \tau_x, \tau_y, \tau_z]^T\in\mathbb{R}^6$ we design in (\ref{eq:control}) is different from the actuator control input $u'(t)=[F, \tau_x, \tau_y, \tau_z]^T\in\mathbb{R}^4$ for UAV since UAV is an underactuated system. The two degrees of freedom we reserved in Section III-A, i.e., $\phi_r$ and $\theta_r$, are just to solve this problem. By substituting $\Theta=\begin{bmatrix}
    \phi_r \\ \theta_r \\ \psi_r
\end{bmatrix}$ into $\begin{bmatrix}
        f_x \\ f_y \\ f_z
\end{bmatrix} = R(\Theta)\begin{bmatrix}
        0 \\ 0 \\ F
\end{bmatrix}$ from UAV dynacmis in (\ref{eq:uav}), the 3 unknown variables $F$, $\phi_r$ and $\theta_r$ can be found from these 3 equations using inverse dynamic because $f_x$, $f_y$, $f_z$ and $\psi_r$ are given. Combining $\phi_r$ and $\theta_r$ with $r'(t)$, we obtain $r(t)= [x_r, y_r, z_r, \phi_r, \theta_r, \psi_r]^T$. For biped robot, we directly have $r'(t)=r(t)\in\mathbb{R}^{12}$ and $u'(t)=u(t)\in\mathbb{R}^{12}$ since biped robot is a fully actuated system. So far, the design of reference trajectory $r(t)$ of each agent in hybrid URTS is done. We define the process of converting $r'(t)$ and $u(t)$ into $r(t)$ and $u'(t)$ mentioned above as the reference generation block in Fig. \ref{fig:tracking}.
\begin{figure*}[htbp]
    \centering
    \includegraphics[scale=.12]{fig/tracking.png}\caption{The flowchart of tracking control in the hybrid URTS.
    (a) The tracking control block of each agent in hybrid URTS. The controller block is predefined in (d). The controller block (the proposed general $H_\infty$ decentralized observer-based feedforward FTC scheme) is designed for a fully actuated agent dynamic model in (\ref{eq:agent}) while the UAV is an underactuated system. It makes the designed control law $u(t)\in\mathbb{R}^6$ and the actuator control input $u'(t)\in\mathbb{R}^4$ different for UAV. The reference generator block is introduced to deal with this problem. For UAVs, the reference generator block is predefined in (b). For robots, the reference generator block is predefined in (c). 
    (b) The reference generator block for each UAV. $u'(t)$ and $r(t)$ can be calculated from $u(t)$ and $r'(t)$ by inverse dynamic through the UAV dynamic model in (\ref{eq:uav}).
    (c) The reference generator block for each robot. $u'(t)=u(t)$ and $r(t)=r'(t)$ since the robot dynamic model in (\ref{eq:robot}) is fully actuated.
    (d) The proposed general $H_\infty$ decentralized observer-based feedforward FTC scheme for each agent in hybrid URTS.}
    \label{fig:tracking}
\end{figure*}

\textit{
    \begin{remark}
        Let $r_{i,j}(t)$ be the reference trajectory $r(t)$, $r_{i,j}[k]$ be the reference path $r[k]$, $(\beta_n)_{i,j}$ be the behavior sequence $(\beta_n)$, $(\sigma_n)_{i,j}$ be the collision-free path $(\sigma_n)$, $q_{start,i,j}$ be the current configuration $q_{start}$, and $q_{goal,i,j}$ be the goal configuration $q_{goal}$ of the agent $\alpha_{i,j}$ in the hybrid URTS. As long as $\alpha_{i,j}$ can track $r_{i,j}(t)$, the hybrid URTS can work as we expect since the previous blocks, i.e, task allocation, path planning, behavior layer and local motion planning, have completed their respective responsibilities and found their corresponding values $q_{start,i,j}$, $q_{goal,i,j}$, $(\sigma_n)_{i,j}$, $(\beta_n)_{i,j}$ and $r_{i,j}[k]$. That is, $r_{i,j}(t)$ is the reference trajectory that can complete the specific task, follow the specific path and perform the specific behavior.
    \end{remark}
}

>>>>

\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.15]{fig/sys.png}\caption{The system architecture of each agent in URTS. The 2 blocks on left hand side are used to convert the low-level sensor information into high-level information, such as map $\mathcal{C}$, current position $q_{start}$ and object information. The 5 blocks on right hand side are the flow of an agent performing a S\&R mission. From the top to the bottom, it is the decision of the goal configuration $q_{qoal}$, the planning of the path $(\sigma_n)$, the decision of the behavior $(\beta_n)$, the planning of the local motion path $r[k]$, and the low-level tracking control. A block with two vertical lines inside in flowchart represents a predefined process which has more detailed subprocesses. The Behavior Layer block is predefined in Fig. \ref{fig:behavior}. The Local Motion Planning block is predefined in Fig. \ref{fig:LMP}. The Tracking Control block is predefined in Fig. \ref{fig:tracking}.}
    \label{fig:sys}
\end{figure}

\subsection{Task Allocation}
In the URTS, it can be expected that each agent $\alpha_{i,j}$ will be assigned to several specific tasks, such as searching a specific area, or delivering supplies to disaster area, etc. However, the number of agents and tasks is more than one, and each agent has different capabilities (e.g., moving speed or load capacity) and state (e.g., the relative distance between the agent itself and the target or the amount of supplies carried), and each task has different characteristics (e.g., urgency, position, amout of supplies needed). Therefore, the results of task allocation can be "good or bad", which leads us to finding the optimal allocation. This problem is referred to a task allocation problem or multi-robot task allocation problem. A problem formulation and a mathematical model of problem can be found in \cite{khamis2015multi}. Although many different formulations and models have been employed to solve the task allocation problem, the common goal is to find a set of agent-task pairs to achieve a specific cost function. In this paper, we assume that the tasks have been properly assigned so that every agent knows a goal $q_{goal}$ it needs to go at every moment.
% $(\mathcal{G})_n, n\in\mathbb{Z}\cap[1, N], N\in\mathbb{Z}^+$
\textit{
    \begin{remark}
        This block is like a commander since it is used to assign task for agents. Thus, if the real S\&R system has human experts as commanders, he can replace its job or make decisions together with it to maximize the rescue value.
    \end{remark}
}
\textit{
    \begin{remark}
        Although each agent has its own team, agents can also work across teams. For example, if the result given by the task allocation algorithm contains the agent-task pairs $(\alpha_{1,5},T_1)$ and $(\alpha_{2,2},T_1)$, then the agent $\alpha_{1,5}$ in team 1 and the agent $\alpha_{2,2}$ in team 2 will execute task $T_1$ together. 
    \end{remark}
}

@@

\subsection{Behavior Layer}
% Since UAVs and robots are real physical systems, they must interact with the environment through a behavior so that they can move and act in the physical world.
Path planning tells agents where to go but not how since we regard the agent as a point. Taking robot as an example, it may walk, run, climb, or jump to follow the path $(\sigma_n)$ according to real scenario. These behaviors with changing position are classified as "moving" behavior in this paper. Besides, the agents in the hybrid URTS do not always moving. Somtimes they have to suspend to take an action (e.g., getting and putting supplies, rotating in place to collect more environment information) or deal with some unexpected situations (e.g., no path found, the robot falls). These behaviors without changing position are classified as "action" behavior in this paper. More behaviors can be added so that the agent can have more ways to act with environment but there must have a corresponding behavior every moment otherwise the agent will lose control. The sequence of these behaviors can be expressed as:
\begin{equation}
    (\beta_n), n\in\mathbb{Z}\cap[1,k_f], \beta_n\in\mathcal{B}
\end{equation}
where $\mathcal{B}$ is the set of behaviors. It means that the path $(\sigma_n)$ is divided into many segments and each segment corresponds to a specific behavior. By the object information in Fig. \ref{fig:sys}, an appropriate behavior can be judged. However, it will be a rather complicated project, so this article will not discuss in detail. The behavior set $\mathcal{B}$ of agents in URTS can be roughly described in Fig. \ref{fig:behavior}.

\begin{figure*}[htbp]
    \centering
    \includegraphics[scale=.12]{fig/behavior.png}\caption{
        (a) The flowchart of Behavior Layer block in Fig. \ref{fig:sys} of each agent in URTS. The behavior to be took at every moment by each agent will be decided in this block. 
        (b) The behavior set of each agent in URTS. The leaves of the tree structure are the possible behaviors an agent can take. For UAVs, the moving behavior set is predefined in (c). For robots, the moving behavior set is predefined in (d). 
        (c) The moving behavior set of each UAV. 
        (d) The moving behavior set of each robot.}%
    \label{fig:behavior}
\end{figure*}

\subsection{Local Motion Planning}
After a specific behavior is determined, the next step is to design a motion to achieve the specific behavior. Local motion planning block is like path planning block but with smaller scale and higher resolution and precision. Collision checking is needed since we consider agent as a point in path planning block but it is a real mechanical body here. Furthermore, the kinodynamic constraint is handled in this block. Although motion planning and path planning are separated into two blocks, the technologies involved are similar and often with the same notion in other literature. Therefore, the output of this block is also a path $r[k]$ (It is also a sequence but this article uses the notation of discrete signal $r[k]$ to represent it). The flowchart of local motion planning block is shown in Fig. \ref{fig:LMP}.
\begin{figure*}[htbp]
    \centering
    \includegraphics[scale=.12]{fig/LMP.png}\caption{
        (a) The flowchart of Local Motion Planning block in Fig. \ref{fig:sys} of each agent in URTS. The corresponding motion planning of an agent will be executed according to the behavior determined by the behavior layer. The exception terminator in figure represents an exceptional condition that performs unconsidered behaviors. The reference path $r[k]$ is a sequence (or discrete signal) designed by a specific behavior block. For UAVs, the moving block is predefined in (b). For robots, the moving block is predefined in (c). 
        (b) The moving block of each UAV where the flying block is predefined in Fig. \ref{fig:FandW}. 
        (c) The moving block of each robot where the walking block is predefined in Fig. \ref{fig:FandW}.}
    \label{fig:LMP}
\end{figure*}

@@

\section{system description of UAVs and biped robots in URTS}
In order to design a reference trajectory $r(t)$ for the motion of UAV and robot in URTS, their dynamic models must be given first. After the system description of UAV and robot in URTS, the motion planning of flying and walking as shown in Fig. \ref{fig:FandW} will be discussed subsequently and separately in the next two subsections.
\begin{figure*}[htbp]
    \centering
    \includegraphics[scale=.12]{fig/FandW.png}\caption{The flowchart of flying block and walking block in Fig. \ref{fig:LMP}. In both blocks, a smoothed path is obtained by post-processing first. Then the respective motion of behavior is designed. 
    %The final outputs of flying block and walking block are all desired reference path $r[k]$, but its value and dimension will vary according to the dimension of the system model.
    (a) The Flying block in Fig. \ref{fig:LMP} of each UAV . By combining the position path $(\sigma'_n)$ and setting $\phi_d=0$ (let UAV fly without spinning), we have the reference path $r[k]$. 
    (b) The Walking block in Fig. \ref{fig:LMP}of each robot. Follow the process in Section IV-B, we have the reference path $r[k]$.}
    \label{fig:FandW}
\end{figure*}
Before the discussion of the motion planning of these two behaviors, the following assumption is maded.
\textit{
    \begin{assumption} \label{asm:cc again}
        The space between obstacles is large enough to eliminate the need for collision checking again, and the average speed of agents is slow enough to ignore the nonholonomic constraints (the velocity and acceleration constraints).
    \end{assumption}
}
However, for these two behaviors, there exists an inevitable holonomic constraint on the curvature of local motion. Although an accurate reference trajectory without breaking the curvature constraint can be designed, it is not easy to solve this problem. Additionally, it is not nessasry for these two behaviors in URTS since they are uesd to move from one location to another while the effect of error during moving caused by breaking the curvature constraint is relatively insignificant. At the same time, the \textit{Assumption \ref{asm:cc again}} makes sure this error will not cause collision. As an alternative, this problem can be handled by curve fitting which can be regarded as a post-process of the path $(\sigma_n)$. The post-process will appear in the begining of motion planning process of these two behaviors as shown in Fig. \ref{fig:FandW}.

@@

Now, suppose the UAV flying behavior occurs between time step $k_1$ and $k_2$, that is, $\beta_n=\mathit{flying}, n\in\mathbb{Z}\cap[k_1,k_2]$. The corresponding path $(\sigma_n), n\in\mathbb{Z}\cap[k_1,k_2]$ will be smoothed first by linear interpolation and then by cubic spline interpolation, which gives the smoothed path $(\sigma_n'), n\in\mathbb{Z}\cap[k_1,k_2+D(k_2-k_1)], \sigma_n'\in\mathbb{R}^3$, where $D\in\mathbb{Z}$ is the interpolation density. Then, $(\sigma_n')$ will be the position reference path $[
    x_r[k], y_r[k], z_r[k]
]^T$. Subsequently, we consider the orientation reference path, row angle $\phi_r[k]$, pitch angle $\theta_r[k]$ and yaw angle $\psi_r[k]$. $\phi_r[k]$ is set to zero since no need for spinning when flying. $\theta_r[k]$ and $\psi_r[k]$ cannot be set beforehand since UAV is an underactuated system, which will be discussed in the next section. Finally, the reference path $r[k]$ of UAV can be obtained by combining them together, i.e., $r[k] = [
    x_r[k], y_r[k], z_r[k], \phi_r[k]
]^T\in\mathbb{R}^{4}$. The flowchart is shown in Fig. \ref{fig:FandW}.

@@

With 3D-LIPM, we can significantly reduce the amount of computation. Let us define the body frame of biped robot as $\{ \widehat{X_b}, \widehat{Y_b}, \widehat{Z_b} \}$ as in \cite{ourrobot}. Taking the forward direction of biped robot as $\widehat{X_b}$ direction, the left direction as $\widehat{Y_b}$ direction, and the torso direction as $\widehat{Z_b}$ direction in body frame, "Falling" means the moments on the robot in $\widehat{X_b}$ and $\widehat{Y_b}$ direction are not zero. More accuately, the biped robot will not fall if the zero moment point (ZMP) lies in the support polygon, i.e., the convex hull of face of supported foots. The ZMP in $\widehat{X_b}$ direction can be described as \cite{huang2001planning} (The ZMP in the $\widehat{Y_b}$ direction is the same form):
\begin{equation} \label{eq:x_zmp}
    x_{zmp} = \frac{\sum_{i=1}^{12} (m_i(\ddot{z}_i+g)x_i - m_i\ddot{x}_iz_i - I_{iy}\ddot{\Omega}_{iy})}
                   {\sum_{i=1}^{12} m_i(\ddot{z}_i+g)}
\end{equation}
where $m_i$ is the CoM, $x_i, z_i$ are the linear position components, $I_{iy}$ is the inertial component, and $\ddot{\Omega}_{iy}$ is the angular acceleration component of link $i$. However, it is difficult to directly calculate the analytical solution of $q_r(t)$ through (\ref{eq:x_zmp}). Since there exists a complex coordinate transformation between $q_r(t)$ and $x_i, z_i, \ddot{\Omega}_{iy}$. At the same time, it is necessary to ensure that $x_{zmp}$ falls in the support polygon which also has a relationship with $q_r(t)$. To simplify this complex problem, an approximate solution can be derived through 3D-LIPM. We find CoM reference first and then obtain $q_r(t)$ by using inverse kinematic (IK) with given step size, step height, step period and CoM height. Many researchers have used this method to avoid complex calculations for ZMP of the actual robot dynamic model. Although there exists a model error between the actual dynamic model and 3D-LIPM, the design process will be more simple. The overall process is shown in Fig. \ref{fig:FandW}.
% \begin{figure}[htbp]
%     \centering
%     \includegraphics[scale=.3]{fig/walking.pdf}\caption{flowchart of biped robot walking}%
%     \label{fig:walking}
% \end{figure}

@@

To complete the design of reference trajectory $r(t)$ of each agent, a D/A converter is used to transform the reference path $r[k]$ (output of local motion planning) into a continuous signal $r'(t)$ as shown in Fig. \ref{fig:tracking}. For UAV, we get $r'(t) = [x_r, y_r, z_r, \phi_r]^T\in\mathbb{R}^{4}$. Besides, for an UAV in hybrid URTS, it can be seen that the control input $u(t)=[f_u^T, \tau_u^T]^T = [f_x, f_y, f_z, \tau_x, \tau_y, \tau_z]^T\in\mathbb{R}^6$ we design in (\ref{eq:control}) is different from the actuator control input $u'(t)=[F, \tau_x, \tau_y, \tau_z]^T\in\mathbb{R}^4$ for UAV since UAV is an underactuated system. The two degrees of freedom we reserved in Section III-A, i.e., $\phi_r$ and $\theta_r$, are just to solve this problem. By substituting $\Theta=\begin{bmatrix}
    \phi_r \\ \theta_r \\ \psi_r
\end{bmatrix}$ into $\begin{bmatrix}
        f_x \\ f_y \\ f_z
\end{bmatrix} = R(\Theta)\begin{bmatrix}
        0 \\ 0 \\ F
\end{bmatrix}$ from UAV dynacmis in (\ref{eq:uav}), the 3 unknown variables $F$, $\phi_r$ and $\theta_r$ can be found from these 3 equations using inverse dynamic because $f_x$, $f_y$, $f_z$ and $\psi_r$ are given. Combining $\phi_r$ and $\theta_r$ with $r'(t)$, we obtain $r(t)= [x_r, y_r, z_r, \phi_r, \theta_r, \psi_r]^T$. For biped robot, we directly have $r'(t)=r(t)\in\mathbb{R}^{12}$ and $u'(t)=u(t)\in\mathbb{R}^{12}$ since biped robot is a fully actuated system. So far, the design of reference trajectory $r(t)$ of each agent in hybrid URTS is done. We define the process of converting $r'(t)$ and $u(t)$ into $r(t)$ and $u'(t)$ mentioned above as the reference generation block in Fig. \ref{fig:tracking}.
\begin{figure*}[htbp]
    \centering
    \includegraphics[scale=.12]{fig/tracking.png}\caption{
    (a) The flowchart of Tracking Control block in Fig. \ref{fig:sys} of each agent in hybrid URTS. The controller block is predefined in (d). The controller block (the proposed general $H_\infty$ decentralized observer-based feedforward FTC scheme) is designed for a fully actuated agent dynamic model in (\ref{eq:agent}) while the UAV is an underactuated system. It makes the designed control law $u(t)\in\mathbb{R}^6$ and the actuator control input $u'(t)\in\mathbb{R}^4$ different for UAV. The reference generator block is introduced to deal with this problem. For UAVs, the reference generator block is predefined in (b). For robots, the reference generator block is predefined in (c). 
    (b) The reference generator block for each UAV. $u'(t)$ and $r(t)$ can be calculated from $u(t)$ and $r'(t)$ by inverse dynamic through the UAV dynamic model in (\ref{eq:uav}). 
    (c) The reference generator block for each robot. $u'(t)=u(t)$ and $r(t)=r'(t)$ since the robot dynamic model in (\ref{eq:robot}) is fully actuated. 
    (d) The proposed general $H_\infty$ decentralized observer-based feedforward FTC scheme for each agent in hybrid URTS.}
    \label{fig:tracking}
\end{figure*}

\textit{
    \begin{remark}
        Since this article analyzes each agent $\alpha_{i,j}$ individually, the subscripts $i$ and $j$ of the corresponding variables are omitted. For example, $x_{i,j}(t)$ is omitted as $x(t)$ in (\ref{eq:agent}), $r_{i,j}(t)$ is omitted as $r(t)$ in (\ref{eq:control}), etc.
    \end{remark}
}
\textit{
    \begin{remark}
        Let $r_{i,j}(t)$ be the reference trajectory $r(t)$ of the agent $\alpha_{i,j}$, $r_{i,j}[k]$ be the reference path $r[k]$ of the agent $\alpha_{i,j}$, $(\beta_n)_{i,j}$ be the behavior sequence $(\beta_n)$ of the agent $\alpha_{i,j}$, $(\sigma_n)_{i,j}$ be the collision-free path $(\sigma_n)$ of the agent $\alpha_{i,j}$, $q_{goal,i,j}$ be the goal configuration $q_{goal}$ of the agent $\alpha_{i,j}$, etc. As long as $\alpha_{i,j}$ can track $r_{i,j}(t)$, the hybrid URTS can work as we expect since the previous blocks, i.e, task allocation, path planning, behavior layer and local motion planning, have completed their respective responsibilities and found their corresponding values, $q_{goal,i,j}$, $(\sigma_n)_{i,j}$, $(\beta_n)_{i,j}$ and $r_{i,j}[k]$. That is, $r_{i,j}(t)$ is the reference trajectory that can complete the specific task, follow the specific path and perform the specific behavior.
    \end{remark}
}

To make the model more realistic, the following external disturbances encountered in actual scenarios are considered:
\begin{enumerate}
    \item For each agent, there exists coupling effect due to co-channel interference in communication between agents \cite{9834947}.
    \item For each agent, there exists cyber-attack on communication network between agents and ground station.
    \item For each agent, there exists sensor noise.
    \item For each UAV, there exists wind disturbance \cite{9075385}.
    \item For each robot, there exists ground reaction force \cite{chen2013human}. 
\end{enumerate}
Let $x_{i,j}(t), i=1,2,\dots,N_T, j=1,2,\dots,N_A$ denote the state vector of agents $\alpha_{i,j}$. The coupling disturbance $c_{i,j}(t)$ on each agent in hybrid URTS can be represented as \begin{equation} \label{eq:UAV couple}
    c_{i,1}(t) = \sum_{k = 1, k \neq i}^{N_T}D_{i, 1, k}(x_{i, 1}(t))x_{k, 1}(t)
\end{equation} for UAV $\alpha_{i, 1}$ and \begin{equation} \label{eq:robot couple}
    c_{i,j}(t) = \sum_{k = 1, k \neq j}^{N_A}D_{i, j, k}(x_{i, j}(t))x_{i, k}(t)
\end{equation} for biped robot $\alpha_{i, j}$ where $i=1,2,\dots,N_T$ and $j=2,3,\dots,N_A$ \cite{9834947}. For the convenience of reading, we use $c(t)$ to represent $c_{i,j}(t)$. Since the ground station is responsible for the calculation, the calculated control command in (\ref{eq:control}) will be transmitted to the agent through the network channel in hybrid URTS. Therefore, the coupling effect due to co-channel interference and the cyber-attack signal will deteriorate the control command. In addition, the wind disturbance and the ground reaction force will apply extra force on an agent in (\ref{eq:agent}). Therefore, through appropriate conversion, the above disturbances can be equivalent to two disturbance forces $c(t)$ + $d_1(t)\in\mathbb{R}^n$ where $d_1(t)$ is the non-coupling disturbance. The nominal system in (\ref{eq:agent}) of an agent in hybrid URTS then be rewrited as the following real system:
% The coupling effect for an agent \textit{$agent_{i,j}$} in URTS can be expressed as the form $\sum_{i'=1,i'\neq i}^{N_i}\sum_{j'=1,j'\neq j}^{N_j}\textit{c}_{i,j}(x_{i,j}(t))\times x_{i',j'}(t)$ where $x_{i,j}(t)$ is the own state.
\begin{equation} \label{eq:agent d1} 
    M(x(t))\ddot{x}(t) + H(x(t),\dot{x}(t)) = u(t) + c(t) + d_1(t)
\end{equation}
% \subsubsection{Internal uncertainties}
% In practice, there is uncertaintiey in the parameters of inertia matrix $M$, Coriolis and centripetal force vector $C$, gravitational force vector $G$, and friction vector $F$. Its effect can be expressed as:
% \begin{equation} \label{eq:internal}
%     \begin{split}
%         &M = M_0 + \Delta M, C = C_0 + \Delta C
%         \\
%         &G = G_0 + \Delta G, F = F_0 + \Delta F
%     \end{split}
% \end{equation}
% where $M_0, C_0, G_0$ and  $F_0$ is the nominal part and $\Delta M,\Delta C,\Delta G$ and $\Delta F$ is the uncertain part.
